The five pillars of computational reproducibility: Bioinformatics and beyond

### 2023-06-16 manuscript/5pillars.Rmd
added t-SNE and UMAP

Another issue is that perfect reproducibility isn't possible in cases where some element of randomness
is requrired by the underlying algorithms.
Such algorithms are extensively used in molecular simulation, machine learning, permutation-based
statistical tests and certain data projection methods, namely t-distributed stochastic neighbour
embedding [@Van_der_Maaten2008-zn] and uniform manifold approximation and projection [@McInnes2018-of],
which are popular for visualising high-dimensional omics data [@Becht2018-ca].
To make such workflows deterministic, the pseudo-random number generator can be initialized with a fixed
value (sometimes called "setting the seed")[@Sandve2013-lk].
However this needs to be done with care to ensure the results do not misrepresent the bulk of
iterations (see [@Benureau2017-uo]).

>>>>

Another issue is that perfect reproducibility isn't possible in cases where some element of randomness
is requrired by the underlying algorithms.
Such algorithms are extensively used in molecular simulation, machine learning, permutation-based
statistical tests and certain data projection methods, namely t-distributed stochastic neighbour
embedding (t-SNE) [@Van_der_Maaten2008-zn] and uniform manifold approximation and projection UMAP [@McInnes2018-of],
which are popular for visualising high-dimensional omics data [@Becht2018-ca].
To make such workflows deterministic, the pseudo-random number generator can be initialized with a fixed
value (sometimes called "setting the seed")[@Sandve2013-lk].
However this needs to be done with care to ensure the results do not misrepresent the bulk of
iterations (see [@Benureau2017-uo]).
